Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-08-30 ms.tex
giving a use case of photon noise to compare with 1/f noise.

>>>>

For a concrete example, we consider a primary transit of WASP-80 b observed with the F444W grism time series mode.
The exposure parameters that give a peak pixel count of 35,000 DN or 40\% well depth are a 2048$\times$256 stripe mode with BRIGHT1 read mode for 12 groups.
These integrations are 31 seconds in duration.
Each integration will have a 7.8$\times 10^7$ DN in a broadband aperture, so the photon noise per integration is 6,500 DN or 83 ppm.
Over 1 hour (111 integrations), the photon noise will be 8 ppm if all integrations are independent.
